Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-26 manuscript.Rmd
Tweaking last figure.

journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))

@@

>>>>

journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))
```

```{r plotPareto}
pareto.df <- df1 %>% group_by(journal) %>% 
    summarize(EBP.counts = sum(N)) %>% 
    arrange(desc(EBP.counts)) %>%
    ungroup() %>%
    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
    mutate(cumSum = cumsum(percentTotal)) %>%
    slice(1:16)

df1.reduced <- na.omit(df1[df1$journal %in% pareto.df$journal, ])
df1.reduced <- ungroup(df1.reduced)
df1.reduced <- full_join(df1.reduced, pareto.df, by = "journal")

#df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))

j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)])

df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)

df1.unique <- group_by(df1.reduced, journal) %>% slice(1)
df1.unique$journal <- factor(df1.unique$journal, levels = j.order)

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = journal, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity") +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = journal, label = EBP.counts), size = 3) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) 
```

@@

proportionsEBP.df <- df1.reduced %>% 
    group_by(journal) %>% 
    slice(1) %>%
     mutate(Journal = as.character(journal)) %>%
    ungroup() %>%
    select(-studyType, -N, -N.sort, -journal, -overallCount, -percentTotal, -cumSum)

proportionEBP2.df <- full_join(proportionsEBP.df, sm.scopus.merged.table, by = "Journal")  %>% 
    mutate(journalProp = EBP.counts / DataBase.N) %>%
    arrange(desc(journalProp))
